### 2020-05-29 1_introduction.tex
Fiddle with text.
More fiddling with wording.

Existing approaches to comparing performance focus on \emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus directly inherit its
behaviors, while benchmarks are typically chosen to reflect a more
narrow set of behaviors. In either case, while a variety of insight
can be gained, the overall effort required is proportional to the
product of the number of systems and behaviors one would like to
evaluate. As a result, few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.

>>>>

Existing approaches to comparing performance focus on \emph{proxy-}/\emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus directly inherit its
properties, while benchmarks are typically chosen to reflect a more
narrow set of behaviors. In either case, while a variety of insight
can be gained, the overall effort required is proportional to the
product of the number of systems and behaviors one would like to
evaluate. As a result, few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.
